Multiset-trie data structure

### 2019-03-11 tex/tex/s_intro.tex
first pass through the 2nd part of the paper (see text about parts).

\section{Introduction} \label{c:introduction}
%
% general intro into problem
%
A multiset is a data structure that represents a collection of elements. It generalizes a set data structure by allowing duplicate elements in a collection. Multisets appear in a wide variety of domains and applications. The index structures for storing sets of multisets were studied in the area of object-relational database systems to efficiently store, compress and query multiset-valued attributes \cite{bouros2016set,gripon2012compressing,ross2004symmetric,steinruecken2015compressing}. Furthermore, the need to efficiently store and query the multisets appears also in the information retrieval \cite{manningBook}, the data mining \cite{interestingSets}, and in the area of expert systems \cite{reteAlgorithm}. 
%
% problem

@@

% description of innovations
%
To improve the efficiency of containment operations, we propose a data structure \emph{multiset-trie} that is designed for storage and processing of a finite bounded set of multisets. It extends the \emph{set-trie} data structure proposed by Savnik~\cite{savnik2013index} that was designed for storage and processing of a finite bounded (?or unbounded?) set of sets. 
%
Set-trie is a trie based data structure that provides a fast search and retrieval of sets and implements set-containment operations. 
%
Multiset-trie generalizes set-trie and can work with a set of sets (as set-trie) or with 
a set of multisets providing efficient multiset-containment operations.

% intro into mstrie
The multiset-trie is an $n$-ary tree based data structure with properties similar to those of a trie. 
Multisets are associated with a collection of nodes in a tree such that every node represents an element 
of a multiset with particular multiplicity bounded by a node degree $n.$
%
Multiset-trie is a kind of search tree. Similarly to a trie, it uses common prefixes for shared data representation.
Unlike the compact prefix tree, the multiset-trie does not support path compression. However, the absence of path 
compression makes the multiset-trie a perfectly height-balanced tree. Moreover, when multiset-trie is full it forms 
a complete $n$-ary tree.
%
The multiset-trie handles multisets directly by having access to each of the element 
without the need to reconstruct them for processing, which allows fast retrieval and 
containment operations. In particular, it supports submultiset and supermultiset queries.
The operations allow to find and retrieve the closest submultisets or supermultisets 
as well as to find and retrieve all of them.

% --------------------------------------------------------------------------------------------------------------------------------------------------------------------

@@

% --------------------------------------------------------------------------------------------------------------------------------------------------------------------

>>>>

\section{Introduction} \label{c:introduction}
%
% general intro into problem
%
A multiset is a data structure that represents a collection of elements. It generalizes a set data structure by allowing duplicate elements in a collection. Multisets appear in a wide variety of domains and applications. The index structures for storing sets of multisets were studied in the area of object-relational database systems to efficiently store, compress and query multiset-valued attributes \cite{bouros2016set,gripon2012compressing,ross2004symmetric,steinruecken2015compressing}. Furthermore, the need to efficiently store and query the multisets appears also in the information retrieval \cite{manningBook}, the data mining \cite{interestingSets}, and in the area of expert systems \cite{reteAlgorithm}. 
%
% problem definition

@@

% description of contributions
%
To improve the efficiency of containment operations, we propose a data structure \emph{multiset-trie} that is designed for the storage and processing of a finite bounded set of multisets. It extends the \emph{set-trie} data structure proposed by Savnik~\cite{savnik2013index} that was designed for storage and processing of a finite bounded (?or unbounded?) set of sets. 
%
Set-trie is a tree data structure that provides a fast search and retrieval of sets and implements set-containment operations. 
%
Multiset-trie generalizes set-trie data structure. It provides a space efficient representation of a set of multisets and, it provides efficient multiset-containment operations. In addition, it can also represent and query sets of sets.

% intro into mstrie
The multiset-trie is an $n$-ary tree data structure. ((letters are levels of tree; each level states 0-n leters; I will correct and balance this further)) Multisets are represented with a collection of nodes in a tree such that every node represents an element of a multiset with particular multiplicity bounded by a node degree $n.$
%
Multiset-trie is also a kind of search tree. Similarly to a trie, it uses common prefixes for a shared data representation. Unlike the compact prefix tree \cite{patriciaTree} ((radix tree?)), the multiset-trie does not support path compression. However, the absence of path compression makes the multiset-trie a perfectly height-balanced tree. Moreover, when multiset-trie is full it forms a complete $n$-ary tree.
%
((this needs to be rewritten)) The multiset-trie handles multisets directly by having access to each of the element without the need to reconstruct them for processing, which allows fast retrieval and containment operations. In particular, it supports submultiset and super-multiset queries. The operations allow to find and retrieve the closest submultisets or super-multisets as well as to find and retrieve all of them.

% --------------------------------------------------------------------------------------------------------------------------------------------

@@

% --------------------------------------------------------------------------------------------------------------------------------------------
